Bandit Multiclass Linear Classification: \\ Efficient Algorithms for the Separable Case

### 2019-01-23 ICML-submission/related-work.tex
tweaked related work

The general problem of linear bandit multiclass learning has received considerable attention~\cite{Abernethy-Rakhlin-2009, Wang-Jin-Valizadegan-2010,
Crammer-Gentile-2013, Hazan-Kale-2011, Beygelzimer-Orabona-Zhang-2017,
Foster-Kale-Luo-Mohri-Sridharan-2018}. \citet{Chen-Lin-Lu-2014,
Zhang-Jung-Tewari-2018} study online bandit multiclass boosting under bandit
feedback, where one can view boosting as linear classification by treating each
base hypothesis as a separate feature.  
%However, most of these works achieve a
%regret of order $\widetilde{O}(\sqrt{T})$ to $O(T^{3/4})$.  
In the weakly linearly separable setting, however, 
these algorithms can guarantee a mistake 
bound of ${O}(\sqrt{T})$ at best.
%One exception is the \textsc{Newtron} algorithm, which---with
%an appropriate setting of parameter $\alpha$---can achieve a $O(\ln T)$
%regret against the $\alpha$-logistic loss. However, as argued in
%~\citep[][Appendix D]{Beygelzimer-Orabona-Zhang-2017}, if the setting of
%$\alpha$ makes the regret bound $O(\sqrt{T})$, the $\alpha$-logistic loss of the
%best linear predictor would be $\Omega(T^{3/4})$. Therefore, \textsc{Newtron} at
%best guarantees a mistake upper bound of $O(\sqrt{T})$ in the weakly linearly
%separable setting.

@@

The problem considered here is a special case of the
contextual bandit problem~\citep{Auer-2003, Langford-Zhang-2008}. 
In this general problem, there is a hidden cost vector $c_t$ associated with every prediction in $\{1,\ldots,K\}$ in round $t$.  Upon receiving $x_t$ and predicting $\widehat{y}_t \in \{1,\ldots,K\}$, the learner gets to observe the incurred cost $c_t(\widehat{y}_t)$.   
The goal of the learning is to minimize its regret with respect to the best predictor in some predefined policy class $\Pi$, given by $\sum_{t=1}^T c_t(\widehat{y}_t) -
\min_{\pi \in \Pi} \sum_{t=1}^T c_t(\pi(x_t))$.
Bandit multiclass learning is a special case
where the cost $c_t(i)$ is the classification error $\indicator{i \neq y_t}$ and 
the policy class is the set of linear classifiers $\cbr{x \mapsto \argmax_y (Wx)_y: W \in \R^{k \times d}}$.
There has been significant progress on the general contextual bandit problem, 
assuming access to an optimization oracle that returns a policy in $\Pi$ with the smallest total cost on any given set of cost-sensitive examples~\citep{Dudik-Hsu-Kale-Karampatziakis-Langford-Reyzin-Zhang-2011,
Agarwal-Hsu-Kale-Langford-Li-Schapire-2014, Rakhlin-Sridharan-2016,
Syrgkanis-Krishnamurthy-Schapire-2016,
Syrgkanis-Luo-Krishnamurthy-Schapire-2016}.
While solving a more general problem that does not make assumptions on the structure of the cost vector $c_t$ or the policy class, these results assume that $x_t$s or $(x_t,c_t)$s are generated i.i.d., in addition to assuming oracle access to search through $\Pi$, neither of which we assume here.

>>>>

The general problem of linear bandit multiclass learning has received considerable attention~\cite{Abernethy-Rakhlin-2009, Wang-Jin-Valizadegan-2010,
Crammer-Gentile-2013, Hazan-Kale-2011, Beygelzimer-Orabona-Zhang-2017,
Foster-Kale-Luo-Mohri-Sridharan-2018}. \citet{Chen-Lin-Lu-2014,
Zhang-Jung-Tewari-2018} study online bandit multiclass boosting under bandit
feedback, where one can view boosting as linear classification by treating each
base hypothesis as a separate feature.  
%However, most of these works achieve a
%regret of order $\widetilde{O}(\sqrt{T})$ to $O(T^{3/4})$.  
In the weakly linearly separable setting, however, 
these algorithms can only guarantee a mistake 
bound of ${O}(\sqrt{T})$ at best.
%One exception is the \textsc{Newtron} algorithm, which---with
%an appropriate setting of parameter $\alpha$---can achieve a $O(\ln T)$
%regret against the $\alpha$-logistic loss. However, as argued in
%~\citep[][Appendix D]{Beygelzimer-Orabona-Zhang-2017}, if the setting of
%$\alpha$ makes the regret bound $O(\sqrt{T})$, the $\alpha$-logistic loss of the
%best linear predictor would be $\Omega(T^{3/4})$. Therefore, \textsc{Newtron} at
%best guarantees a mistake upper bound of $O(\sqrt{T})$ in the weakly linearly
%separable setting.

@@

The problem considered here is a special case of the
contextual bandit problem~\citep{Auer-2003, Langford-Zhang-2008}. 
In this general problem, there is a hidden cost vector $c_t$ associated with every prediction in round $t$.  Upon receiving $x_t$ and predicting $\widehat{y}_t \in \{1,\ldots,K\}$, the learner gets to observe the incurred cost $c_t(\widehat{y}_t)$.  
The goal of the learner is to minimize its regret with respect to the best predictor in some predefined policy class $\Pi$, given by $\sum_{t=1}^T c_t(\widehat{y}_t) -
\min_{\pi \in \Pi} \sum_{t=1}^T c_t(\pi(x_t))$.
Bandit multiclass learning is a special case
where the cost $c_t(i)$ is the classification error $\indicator{i \neq y_t}$ and 
the policy class is the set of linear classifiers $\cbr{x \mapsto \argmax_y (Wx)_y: W \in \R^{k \times d}}$.
There has been significant progress on the general contextual bandit problem
assuming access to an optimization oracle that returns a policy in $\Pi$ with the smallest total cost on any given set of cost-sensitive examples~\citep{Dudik-Hsu-Kale-Karampatziakis-Langford-Reyzin-Zhang-2011,
Agarwal-Hsu-Kale-Langford-Li-Schapire-2014, Rakhlin-Sridharan-2016,
Syrgkanis-Krishnamurthy-Schapire-2016,
Syrgkanis-Luo-Krishnamurthy-Schapire-2016}.
While solving a more general problem without making assumptions on the structure of the cost vector $c_t$ or the policy class, these results assume that $x_t$ vectors or $(x_t,c_t)$ pairs are generated i.i.d. and that such an oracle abstracting efficient search through $\Pi$ is available---neither of which we assume here.
